\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-18 evaluation.tex
Fabric stuff

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics from modeling the environment of the three Microsoft Azure-based systems under test.}
\label{tab:stats}
%\vspace{-3mm}
\end{table}

@@

Modeling Fabric required approximately 5 person months. Although this is a
significant amount of time, it is a one time effort (once per release). \PDComment{should say that 5 months is required for release 1.0, subsequent releases should be much faster} Our plan is to reuse the developed Fabric model 
for testing arbitrary user services built for the Azure Service Fabric system.

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics from modeling the environment of the three Microsoft Azure-based systems under test. The ($\star$) denotes ``awaiting confirmation''.}
\label{tab:stats}
%\vspace{-3mm}
\end{table}

@@

Modeling Fabric required approximately $5$ person months. Although this is a
significant amount of time, it is a one time effort, which only needs incremental refinement with each release.

### 2015-09-18 experience.tex
Fabric stuff

Azure Service Fabric\footnote{\url{azure.microsoft.com/campaigns/service-fabric/}} (or Fabric for short) is a platform and API for creating reliable services that execute on a cluster of machines. 
%The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. 
In order to make the user-written service \emph{reliable}, Fabric launches several \emph{replicas} (copies) of the service, where each replica runs as a separate process on a different node in the cluster.
%\PTComment{Cut: description of primary and secondaries, and electing a new primary.}
%One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries by sending \emph{replication requests} so that all replicas eventually have the same state. If the primary fails (e.g.\ if the node on which the primary is running crashes), Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive a full or partial copy (depending on whether persistent storage is used) of the state of the new primary in order to ``catch up'' with the other secondaries. Fabric provides a name-resolution service so that clients can always find the current primary.
The state of the service is replicated from the \emph{primary} replica to the other \emph{secondary} replicas for redundancy.
Since user-written Fabric services are complex asynchronous and distributed applications, 
they are challenging to test.
% They are interesting targets for systematic testing with \psharp{}.

Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The model is written once
to include all behaviours of Fabric
so that it can be used again and again to test arbitrary Fabric services.
This was the largest among the case studies
and required multiple rounds of debugging.
The availability of systematic testing
allowed us to debug the model to
a point where reported assertion violations indicate a bug in the
user service.
Without systematic testing,
even bugs in the model would have been hard to find.
Note that we model the lowest Fabric API layer (\texttt{Fabric.dll})
which is not documented for use externally.
Eventually, we will lift the model
to higher layers
but for this paper we study internally-developed services
that target the lowest layer.

@@

The main system that we tested is 
\emph{CScale}~\cite{faleiro2012},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
A key challenge was that
CScale contains inter-service communication.
%\PTComment{Cut: detail.}
% that resolves services
% via Fabric but communicates
% using a non-Fabric remote procedure call protocol.
To close the system,
%\PTComment{Cut: we implemented service resolution}
% we first implemented service resolution in our Fabric model,
% which resolves Fabric service names to IP addresses.
%We then replaced 
we 
replaced the relevant classes
% replaced the inter-service communication classes with our own,
% ;
% our replacement includes the ability to map
% URLs to \psharp{} machines
so that remote procedure calls are implemented
by sending and receiving \psharp{} events.
Thus,
we converted a distributed system
that uses both Fabric and its own
network communication protocol
% that runs on the Fabric platform
% and 
% uses network communication
into 
a closed single process system. 
% that uses multiple threads,
% contains
% the Fabric model
% and the CScale services,
% and does not use network communication.
%\PTComment{Cut: we had to remove static fields.}
% Additional changes were needed to
% remove certain static (per-process) fields,
% as these were inadvertently
% being shared between services
% after making the system a single process.
A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However,
we were able to find a \texttt{NullReferenceException}
bug
in CScale
by running it on our model.

>>>>

Azure Service Fabric\footnote{\url{azure.microsoft.com/campaigns/service-fabric/}} (or Fabric for short) is a platform and API for creating reliable services that execute on a cluster of machines. 
%The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. 
In order to make the user-written service \emph{reliable}, Fabric launches several \emph{replicas} (copies) of the service, where each replica runs as a separate process on a different node in the cluster.
%\PTComment{Cut: description of primary and secondaries, and electing a new primary.}
%One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries by sending \emph{replication requests} so that all replicas eventually have the same state. If the primary fails (e.g.\ if the node on which the primary is running crashes), Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive a full or partial copy (depending on whether persistent storage is used) of the state of the new primary in order to ``catch up'' with the other secondaries. Fabric provides a name-resolution service so that clients can always find the current primary.
The state of the service is replicated from the \emph{primary} replica to the other \emph{secondary} replicas for redundancy.
User-written Fabric services are complex asynchronous and distributed applications and are, thus,
challenging to test.
% They are interesting targets for systematic testing with \psharp{}.

Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The model is written once
to include all behaviours of Fabric, including simulating failures and recovery,
so that it can be reused repeatedly to test multiple Fabric services.
This was the largest modeling exercise among the case studies but the cost
was amortized across testing multiple servies. This is analogous to the work
on driver verification \cite{BallLR11} where the cost of developing a model
of the Windows kernel was amortized across testing multiple device drivers.
Note that we model the lowest Fabric API layer (\texttt{Fabric.dll})
which is currently not documented for use externally.
We target internally-developed services that invoke the lowest layer.

\psharp's systematic testing was very helpful in debugging the model itself.
Without systematic testing, we feel even catching bugs in the model 
would have been difficult.

@@

The main system that we tested is \emph{CScale}~\cite{faleiro2012},
a big data-stream processing system. In prior work~\cite{deligiannis2015psharp}, 
we used an earlier version of the Fabric model and reported bugs in sample serives.
Supporting CScale required significant additions to the model, making it much more
feature complete.
CScale chains multiple Fabric services, which communicate via remote procedure calls (RPCs).
To close the system, we modeled RPCs 
by sending and receiving \psharp{} events.
This was enough to converted a distributed system
that uses both Fabric and its own
network communication protocol
% that runs on the Fabric platform
% and 
% uses network communication
into 
a closed single process system. 
% that uses multiple threads,
% contains
% the Fabric model
% and the CScale services,
% and does not use network communication.
%\PTComment{Cut: we had to remove static fields.}
% Additional changes were needed to
% remove certain static (per-process) fields,
% as these were inadvertently
% being shared between services
% after making the system a single process.
A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However, we were able to find a \texttt{NullReferenceException}
bug in CScale by running it on our model. The bug has been
communicated to the developers of CScale, but we are still awaiting a
confirmation.
